Parsing Postfix log files

### 2008-05-03 doc/logparser-parsing-algorithm.tex
Mention that Outlook makes aborted delivery attempts.

Some mail clients behave unexpectedly during the \SMTP{} dialogue: the
client aborts the first delivery attempt after the first recipient is
accepted, then makes a second delivery attempt for the same recipient which
it continues with until delivery is complete.  An example dialogue
exhibiting this behaviour is shown presented below (lines starting with a
three digit number are sent by the server, the other lines are sent by the
client):

>>>>

Some mail clients behave unexpectedly during the \SMTP{} dialogue: the
client aborts the first delivery attempt after the first recipient is
accepted, then makes a second delivery attempt for the same recipient which
it continues with until delivery is complete.\footnote{Microsoft Outlook is
one client which behaves in this fashion; no attempt has been made to
identify other clients which act in a similar way.}  An example dialogue
exhibiting this behaviour is presented below (lines starting with a three
digit number are sent by the server, the other lines are sent by the
client):
